### 2019-10-16 ch0_frontmatter.tex
update thesis

%\newpage{\thispagestyle{empty}\cleardoublepage}
%\chapter*{Acknowledgements}

@@

%\newpage{\thispagestyle{empty}\cleardoublepage}
%\listoffigures

%\newpage{\thispagestyle{empty}\cleardoublepage}
%\listoftables

@@

\chapter*{Summary}

Recent technological developments triggered a major milestone in cellular biology by being able to profile and monitor biomolecular contents of single cells at a genome-wide level. The rapid advancements in single-cell omics allow for new types of analyses that fundamentally redefine our understanding of cellular heterogeneity and dynamic processes. Even now, there are even more exciting advancements on the horizon, with the Human Cell Atlas aiming to create a biomolecular and spatial map of all the different cell types in the body.

@@

\chapter*{Samenvatting}

Recente technologische ontwikkelingen hebben geleid tot significante ontwikkelingen in celbiologie die ons toelieten om de biomoleculaire inhoud van individuele cellen op een genoomwijde manier te observeren. Dankzij snelle ontwikkelingen in \textit{single-cell omics} technologieën wordt ons verstaan van cellulaire heterogeniteit en dynamische processen voortdurend gewijzigd. Inmiddels zijn er nieuwe spannende ontwikkelingen onderweg, zoals het \textit{Human Cell Atlas} project, die mikt om alle celtypes in het menselijke lichaam op biomoleculaire en spatiële wijze in kaart te brengen.

>>>>

@@

@@

\chapter*{Summary}
\vspace{-4em}
Recent technological developments triggered a major milestone in cellular biology by being able to profile and monitor biomolecular contents of single cells at a genome-wide level. The rapid advancements in single-cell omics allow for new types of analyses that fundamentally redefine our understanding of cellular heterogeneity and dynamic processes. Even now, there are even more exciting advancements on the horizon, with the Human Cell Atlas aiming to create a biomolecular and spatial map of all the different cell types in the body.

@@

\chapter*{Samenvatting}
\vspace{-4em}
Recente technologische ontwikkelingen hebben geleid tot significante ontwikkelingen in celbiologie die ons toelieten om de biomoleculaire inhoud van individuele cellen op een genoomwijde manier te observeren. Dankzij snelle ontwikkelingen in \textit{single-cell omics} technologieën wordt ons verstaan van cellulaire heterogeniteit en dynamische processen voortdurend gewijzigd. Inmiddels zijn er nieuwe spannende ontwikkelingen onderweg, zoals het \textit{Human Cell Atlas} project, die mikt om alle celtypes in het menselijke lichaam op biomoleculaire en spatiële wijze in kaart te brengen.
